---
title: "Demand Estimation using market data - 1"
author: "Agraj Gupta"
date: "April 11, 2018"
output: html_document
---


```{r Library and H2O setup}
# Packages and h2o setup 
rm(list = ls())
.libPaths(new = c("Y:/agrajg/Research/Paper1/packrat/lib/x86_64-w64-mingw32/3.4.3",
                  "H:/agrajg/R", 
                  "H:/agrajg/R2")) 
library(tibble)
library(dplyr)
library(magrittr)
library(caret)
library(ggplot2)
library(tidyverse)
library(ggthemes)
library(h2o)
localH2O <- h2o.init(nthreads = -1,max_mem_size = '265g' ,port =54326)
```


```{r Loading and initial date prep, include=FALSE}
rm(list = ls())
# Loading market data
ptm <- proc.time()
load(file = "000001_AIRDNA_market_data_clean_final.RData")

# removing blocked listings, changing name from MarketARB.df to market.df
market.df <- MarketARB.df %>% 
                  select(-ends_with("alt")) %>% 
                  filter(status != "B")
rm(list = c("MarketARB.df"))
# market.df %>% head()
# market.df %>% tail()

# Converting date into R date format
market.df$date <- as.Date(market.df$date, "%d%b%Y")
# market.df %>% head()
# market.df %>% tail()

# Subsetting the data frame
# market.df %>% filter(date <= "01-01-2015") %>% head()
str(market.df)
market.df <- market.df %>% filter(date < "2015-01-01")
str(market.df)
proc.time() - ptm

# Converting into h2o data frame
ptm <- proc.time()
market.df.h2o <- as.h2o(market.df)
proc.time() - ptm
# Creating formating variables
market.df.h2o$propertyid <- as.factor(market.df.h2o$propertyid)
market.df.h2o$lprice <- log(market.df.h2o$price)
original_colnames <- h2o.colnames(market.df.h2o)
```

This is an exercise to estimate demand for Airbnb host using the market data. Specifically, we are interested in demand for product $j$ in each market indexed by time $t$.  

```{r Output path, include=FALSE}
# Model 1 
# logit of price on quantity
Output_Path = "Y:/agrajg/Research/Paper1/Output/Logit_Demand_Market_Level"
```

Simple logit booking dummy on price, no controls
```{r logit 1}
yvar <- "status"
xvar1 <- c("lprice")
glm.model1 <- h2o.glm(x= xvar1, y=yvar, training_frame=market.df.h2o, family = "binomial",
                  remove_collinear_columns = TRUE,
                  lambda = 0 ,
                  seed = 47374, 
                  objective_epsilon = 0.000001, 
                  max_iterations = 10000, 
                  compute_p_values = FALSE)
# h2o.saveModel(glm.model1, path = paste(Output_Path, "/", "glm.model1", sep = ""), force = TRUE)
h2o.saveModel(glm.model1, path = Output_Path, force = TRUE)
glm.model1@model$coefficients["lprice"]
summary(glm.model1)

```

so the price coefficient $ \beta_p = $ `r glm.model1@model$coefficients["lprice"]`.

Logit - booking dummy on price , property fixed effects
```{r logit 2}
yvar <- "status"
xvar2 <- c("lprice", "propertyid")
glm.model2 <- h2o.glm(x= xvar2, y=yvar, training_frame=market.df.h2o, family = "binomial",
                  remove_collinear_columns = TRUE,
                  lambda = 0 ,
                  seed = 47374, 
                  objective_epsilon = 0.000001, 
                  max_iterations = 10000, 
                  compute_p_values = FALSE)
# h2o.saveModel(glm.model2, path = paste(Output_Path, "/", "glm.model2", sep = ""), force = TRUE)
h2o.saveModel(glm.model2, path = Output_Path, force = TRUE)
glm.model2@model$coefficients["lprice"]
summary(glm.model2)
```

Logit - booking dummy on price , property fixed effects, date fixed effects
```{r logit 3}
# Creating a date factor through string variable
market.df.h2o$datefactor <- as.factor(as.character(market.df.h2o$date))
yvar <- "status"
xvar3 <- c("lprice", "propertyid", "datefactor")
glm.model3 <- h2o.glm(x= xvar3, y=yvar, training_frame=market.df.h2o, family = "binomial",
                  remove_collinear_columns = TRUE,
                  lambda = 0 ,
                  seed = 47374, 
                  objective_epsilon = 0.000001, 
                  max_iterations = 10000, 
                  compute_p_values = FALSE)
# h2o.saveModel(glm.model3, path = paste(Output_Path, "/", "glm.model3", sep = ""), force = TRUE)
h2o.saveModel(glm.model3, path = Output_Path, force = TRUE)
glm.model3@model$coefficients["lprice"]
# Removing date factor variable from the data frame
market.df.h2o <- market.df.h2o[ , original_colnames]
summary(glm.model3)
```

```{r logit 4}
market.df.h2o$year <- as.factor(as.character(year(market.df.h2o$date)))
market.df.h2o$month <- as.factor(as.character(month(market.df.h2o$date)))
pairwise <- h2o.interaction(market.df.h2o, destination_frame = 'pairwise',
                            factors = list(c("propertyid","year"),c("propertyid","month")),
                            pairwise=TRUE, min_occurrence = 1, max_factors = 1000000)
market.df.h2o <- h2o.cbind(market.df.h2o, pairwise)
yvar <- "status"
xvar4 <- c("lprice", "propertyid_year", "propertyid_month")
glm.model4 <- h2o.glm(x= xvar4, y=yvar, training_frame=market.df.h2o, family = "binomial",
                  remove_collinear_columns = TRUE,
                  lambda = 0 ,
                  seed = 47374,
                  objective_epsilon = 0.000001,
                  max_iterations = 10000,
                  compute_p_values = FALSE)
# h2o.saveModel(glm.model3, path = paste(Output_Path, "/", "glm.model3", sep = ""), force = TRUE)
h2o.saveModel(glm.model4, path = Output_Path, force = TRUE)
glm.model4@model$coefficients["lprice"]
summary(glm.model4)

market.df.h2o$datefactor <- as.factor(as.character(market.df.h2o$date))
yvar <- "status"
xvar5 <- c("lprice", "propertyid_year", "propertyid_month", "datefactor")
glm.model5 <- h2o.glm(x= xvar5, y=yvar, training_frame=market.df.h2o, family = "binomial",
                  remove_collinear_columns = TRUE,
                  lambda = 0 ,
                  seed = 47374,
                  objective_epsilon = 0.000001,
                  max_iterations = 10000,
                  compute_p_values = FALSE)
# h2o.saveModel(glm.model3, path = paste(Output_Path, "/", "glm.model3", sep = ""), force = TRUE)
h2o.saveModel(glm.model5, path = Output_Path, force = TRUE)
glm.model5@model$coefficients["lprice"]
summary(glm.model5)

```

